<span style="color:red;">Building a house with<br />Advanced Normalization Tools (*ANTs*)</span>

### 2015-04-29 competitions/competitions.Rmd
ENH:  Finish up competition slides.

@@

![](./competitions/figures/brats2013results.png)

_Optimal symmetric multimodal templates and concatenated random forests for
supervised brain tumor segmentation (simplified) with ANTsR_

@@

![](./competitions/figures/cardiacBSplineSyN.png)

A great opportunity to showcase a [new SyN variant](http://www.ncbi.nlm.nih.gov/pubmed/24409140)

>>>>

![](./competitions/figures/SATA_data.png)

@@

![](./competitions/figures/brats2013results1.png)

![](./competitions/figures/brats2013results2.png)

Optimal symmetric multimodal templates and concatenated random forests for
supervised brain tumor segmentation (simplified) with ANTsR, _Neuroinformatics_.

@@

![](./competitions/figures/image_gallery.gif)

<!--- A great opportunity to showcase a [new SyN variant](http://www.ncbi.nlm.nih.gov/pubmed/24409140) -->
